### 2019-03-07 reports/thesis/chapters/5_inference.tex
Modified inference chapter, added figures

\section{Hypothesis Testing}

@@

\section{Multiple Hypothesis Testing}

@@

\subsection{Examples}

A few numerical examples is shown here to explore the properties of the 3 different types of methods to do multiple hypothesis testing. Two scenarios is shown here. In the first case, 1\,000 $\normal(0,1)$ independent test statistics were simulated, all test statistics were null. In the second case, 800 null $\normal(0,1)$ and 200 non-null $\normal(2,1)$ independent test statistics were simulated.

A histogram of the test statistics in the all null case is shown in Figure \ref{fig:inference_multi_test_nullhisto_pvalues}. The critical boundaries are also shown. In the uncorrected case, the critical region is $\|Z\|>2$. Using the Bonferroni correction, the critical region becomes $\|Z\|>4.08...$. By inspection of the histogram, the uncorrected method tested a number of test statistics to be positive and falsely so. The Bonferroni correction performs well because it tested all the test statistics as negative correctly.

The ordered $p$-values are shown in Figure \ref{fig:inference_multi_test_nullhisto_pvalues}. The $p$-values form a straight line as a result of being uniformly distributed. The critical line is $0.0455...\times\text{order}/1\,000$ using the BH procedure. In the all null case, the $p$-values are all larger than the critical line, thus no test statistic were tested positive using the BH procedure. As a result, the Bonferroni and BH procedure tested all test statistics to be negative correctly.

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.8\textwidth}
    	\includegraphics[width=\textwidth]{../figures/inference/multi_test_nullhisto.eps}
    	\caption{Histogram}
    \end{subfigure}
	\begin{subfigure}[b]{0.8\textwidth}
    	\includegraphics[width=\textwidth]{../figures/inference/multi_test_nullpvalues.eps}
    	\caption{Ordered $p$-values}
    \end{subfigure}
    \caption{1\,000 null test statistics were simulated. a) Critical boundaries are shown at the $z_\alpha=2$ level, one uncorrected for multiple testing, another corrected using the Bonferroni correction. b) Any values below the critical line are declared significant using the BH procedure.}
    \label{fig:inference_multi_test_nullhisto_pvalues}
\end{figure}

In the second scenario, 800 $\normal(0,1)$ and 200 $\normal(2,1)$ test statistics were simulated. The histogram of the simulated test statistics, along with the critical regions, is shown in Figure \ref{fig:inference_multi_test_althisto_pvalues}. The uncorrected and Bonferroni corrected critical regions are still the same as the first scenario. However this time the critical region using the BH procedure is different, it is $\|Z\|\geqslant\input{../tables/multi_test_alt_z_critical.txt}...$.

The ordered $p$-values are shown in Figure \ref{fig:inference_multi_test_althisto_pvalues}. There are $p$-values below the critical line according to the BH procedure. $p$-values below where the curves intersect are considered significant, testing $\input{../tables/multi_test_alt_n_positive_bh.txt}$ test statistics as positive. The uncorrected test tested $\input{../tables/multi_test_alt_n_positive_uncorrected.txt}$ test statistics as positive.

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.8\textwidth}
    	\includegraphics[width=\textwidth]{../figures/inference/multi_test_althisto.eps}
    	\caption{Histogram}
    \end{subfigure}
	\begin{subfigure}[b]{0.8\textwidth}
    	\includegraphics[width=\textwidth]{../figures/inference/multi_test_altpvalues.eps}
    	\caption{Ordered $p$-values}
    \end{subfigure}
    \caption{800 null $\normal(0,1)$ and 200 non-null $\normal(2,1)$ test statistics were simulated. a) Critical boundaries are shown at the $z_\alpha=2$ level, one uncorrected for multiple testing, another corrected using the Bonferroni correction. b) Any values below the critical line are declared significant using the BH procedure.}
    \label{fig:inference_multi_test_althisto_pvalues}
\end{figure}

This example shows a number of things. The BH procedure adapts to the data to control for the FDR. The uncorrected method did produce more positive results but at a cost of more false positives. It may seem unimpressive that the BH procedure only tested $\input{../tables/multi_test_alt_n_positive_bh.txt}$ positive results, but this is to control the FDR or the number of false positives out of all positive results.

Unfortunately not all 200 non-null test statistics were tested as positive, statisticians would describe it as not powerful. This is however unavoidable as a number of null and non-null test statistics will be similar in value. The aim of hypothesis testing is not to classify positive and negative results correctly, but rather highlight a number of test statistics which are worth investigation.

The error rates can be estimated as a result of knowing whenever each test statistic is truly null or non-null. Suppose the simulation was repeated $N$ times and $r_1,r_2,\dotdotdot,r_N$ number of test statistics were observed to be tested positive. From these positive results, suppose in addition that $v_1,v_2,\dotdotdot,v_N$ false positives were observed. In other words, they are realisations of the random variables defined in Table \ref{table:inference_randomvariables}. The error rates can be estimated
\begin{equation}
	\widehat{\text{PCER}} = \frac{1}{Nn}\sum_{i=1}^N v_i
\end{equation}
\begin{equation}
	\widehat{\text{FWER}} = \frac{1}{N} \sum_{i=1}^N \mathbb{I}(v_i\neq 0)
\end{equation}
\begin{equation}
	\widehat{\text{FDR}} = \frac{1}{N}\sum_{i=1}^N\dfrac{v_i}{r_i}\times\mathbb{I}(r_i\neq0)
	\ .
\end{equation}
The estimates of PCER and FDR is essentially the sample mean, so the standard error can be used to quantify the error. For the FWER, the standard error was chosen to be
\begin{equation}
	\text{standard error of }\widehat{\text{FWER}} = 
	\sqrt{\dfrac{ab}{(a+b)^2(a+b+1)}}
\end{equation}
where $a = \sum_{i=1}^N \mathbb{I}(v_i\neq 0)$ and $b = N - a$. Without going into too much detail, this comes from setting a prior $\text{FWER}\sim\betaDist(0,0)$ and assuming that $\mathbb{I}(V\neq0)\sim\bernoulli(\text{FWER})$. The posterior distribution is $\text{FWER}|V_1,V_2,\dotdotdot V_N\sim\betaDist(a,b)$ and the variance was used for the standard error.

\begin{table}
    \centering
    \begin{subtable}{\textwidth}
    	\centering
    	\input{../tables/inference_error_rate1.txt}
    	\caption{1\,000 $\normal(0,1)$}
    \end{subtable}
    \begin{subtable}{\textwidth}
    	\centering
    	\input{../tables/inference_error_rate2.txt}
    	\caption{800 $\normal(0,1)$ and 200 $\normal(2,1)$}
    \end{subtable}
    \caption{Various error rates when using different types of corrections for multiple hypothesis testing at the $z_\alpha=2$ level. 1\,000 test statistics were simulated, in a) all test statistics are null and b) some are non-null. Error bars represent the standard errors after 1\,000 repeats of the experiment.}
    \label{table:inference_error_rate}
\end{table}

Error rates estimations for the two scenarios are shown in Table \ref{table:inference_error_rate} for $N=1\,000$. These estimations show that the 3 different types of multiple hypothesis controls for different error rates. The uncorrected, Bonferroni and BH controls the PCER, FWER and FDR to be equal or below $\alpha\approx 0.455$ respectively, equality is met when all the test statistics are all truly null.

@@

\subsection{More on the Empirical Null}

@@

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/ZNull1.eps}
        \caption{$\mu_0$}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/ZNull2.eps}
        \caption{$\sigma_0$}
    \end{subfigure}
    }
    \caption{Median squared error of the estimators of the empirical null parameters from 50 repeats of $n$ simulated $\normal(0,1)$ data. Lines represent the rule of thumb for various values of $b$.}
    \label{fig:inference_ZNull1}
\end{figure}

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/ZNull3.eps}
        \caption{3D plot}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/ZNull4.png}
        \caption{Heatmap}
    \end{subfigure}
    }
    \caption{Median value of $\widehat{\sigma}_0$ from 50 repeats of $n$ simulated $\normal(0,1)$ data. On the right, lines represent the rule of thumb for various values of $b$. On the left shows the true value of $\sigma_0=1$ as a plane, the empirical truth is where that plan intersects the surface.}
    \label{fig:inference_ZNull2}
\end{figure}

@@

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/ZNull_mseplot1.eps}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/ZNull_mseplot5.eps}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/ZNull_mseplot9.eps}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/ZNull_mseplot12.eps}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/ZNull_mseplot16.eps}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/ZNull_mseplot20.eps}
    \end{subfigure}
    }
    \caption{A local quadratic regression was fitted on the log mean squared error for estimating $\sigma_0$ against the bandwidth. The estimator $\widehat{\sigma}_0$ uses the kernel density estimator fitted onto $n$ simulated standard Normal data. Boxplots were used to represent the variation of the error from 50 repeats.}
    \label{fig:inference_ZNull_mse_plot}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.7\textwidth]{../figures/inference/ZNull_mserule_of_thumb.eps}
	\caption{An identity link Gamma GLM was fitted onto the relationship between the optimal bandwidth and $n^{-1/5}$. The boxplot show the bootstrap error in finding the optimal bandwidth, which is only there for illustration purposes.}
	\label{fig:inference_ZNull_mserule_of_thumb}
\end{figure}

\begin{table}
	\centering
	\input{../tables/ZNull_mse_glm_estimate.txt}
	\caption{Estimated and standard error gradient and intercept from the linear relationship in Figure \ref{fig:inference_ZNull_mserule_of_thumb}.}
	\label{table:inference_ZNull_mse_glm_estimate}
\end{table}

@@

Those familiar with local quadratic regressions would know that a kernel and a smoothness parameter need to be specified \citep{friedman2001elements}. In these plots a Gaussian kernel was used with smoothness parameter $\input{../tables/ZNull_bandwidth.txt}$. The smoothness parameter $\input{../tables/ZNull_bandwidth.txt}$ was chosen from a quick inspection of the curves. The units of the smoothness parameter is not too important here. But one should note that the smoothness parameter would affect the solution to the optimal bandwidth.

To take into the sensitivity to the smoothness parameter, the whole analysis was repeated using various smoothness parameters. The gradient and intercept for various smoothness parameters are shown in Figure \ref{fig:inference_ZNull_msesensitive}. It can seen that the intercept is fairly stable, including the gradient at smoothness parameter around $\input{../tables/ZNull_bandwidth.txt}$.

\begin{figure}
	\centering
	\includegraphics[width=0.7\textwidth]{../figures/inference/ZNull_msesensitive.eps}
	\caption{Finding the relationship between the optimal bandwidth and $n^{-1/5}$ was repeated for various smoothness parameters in the local quadratic regression. Error bars represent the standard error.} 
	\label{fig:inference_ZNull_msesensitive}
\end{figure}

@@

\subsection{Further Discussion}

@@

In this experiment, a Gaussian image of size $\addNumber{../figures/inference/allnull/AllNullGaussian_width.txt} \times \addNumber{../figures/inference/allnull/AllNullGaussian_height.txt}$ was simulated. The sample mean and sample variance of the post filtered test statistics were recorded. This was repeated \addNumber{../figures/inference/allnull/AllNullGaussian_nrepeat.txt} times by simulating another Gaussian image. Various kernel radiuses from $r = \addNumber{../figures/inference/allnull/AllNullGaussian_radius1.txt}$ to $r = \addNumber{../figures/inference/allnull/AllNullGaussian_radiusend.txt}$ were investigated.

\begin{figure}[htp]
	\centering
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussian_mean.eps}
		\caption{Post filter sample mean}
	\end{subfigure}
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussian_variance.eps}
		\caption{Post filter sample variance}
	\end{subfigure}
	\caption{The sample mean and sample variance of the test statistics in a filtered Gaussian image of size $\addNumber{../figures/inference/allnull/AllNullGaussian_width.txt} \times \addNumber{../figures/inference/allnull/AllNullGaussian_height.txt}$. The box plots summarise the \addNumber{../figures/inference/allnull/AllNullGaussian_nrepeat.txt} repeats of the experiment. The dotted lines show the critical region at the 2$\sigma$ level using standard tests for the sample mean and sample variance, assuming independence.}
	\label{fig:inference_allnullgaussian}
\end{figure}

@@

An experiment was conducted to investigate the sample mean and sample variance of the filtered contaminated image. Ideally the sample mean and sample variance should be 0 and 1 respectively. Different radiuses were investigated from $r=\addNumber{../figures/inference/allnull/AllNullPlane_radius1.txt}$ to $r=\addNumber{../figures/inference/allnull/AllNullPlane_radiusend.txt}$ and repeated \addNumber{../figures/inference/allnull/AllNullPlane_nrepeat.txt} times.

@@

\begin{figure}[htp]
	\centering
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlane_mean.eps}
		\caption{Post filter sample mean}
	\end{subfigure}
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlane_variance.eps}
		\caption{Post filter sample variance}
	\end{subfigure}
	\caption{The sample mean and sample variance of the test statistics in a filtered contaminated Gaussian image of size $\addNumber{../figures/inference/allnull/AllNullGaussian_width.txt} \times \addNumber{../figures/inference/allnull/AllNullGaussian_height.txt}$. The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = \addNumber{../figures/inference/contamination/gradx.txt} (x-x_0) + \addNumber{../figures/inference/contamination/grady.txt} (y-y_0)$ and $\sigma_0=\addNumber{../figures/inference/contamination/nullstd.txt}$. The box plots summarise the \addNumber{../figures/inference/allnull/AllNullPlane_nrepeat.txt} repeats of the experiment. The dotted lines show the critical region at the 2$\sigma$ level using standard tests for the sample mean and sample variance, assuming independence.}
	\label{fig:inference_allnullplane}
\end{figure}

@@

\begin{figure}[p]
	\centering
		\centerline{
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare2_imagePreContaminated.eps}
				\caption{Uncontaminated}
			\end{subfigure}
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare2_imageContaminated.eps}
				\caption{Contaminated}
			\end{subfigure}
		}
		\centerline{
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare2_imageFiltered.eps}
				\caption{Filtered}
			\end{subfigure}
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare2_nullMean.eps}
				\caption{Empirical null mean}
			\end{subfigure}
		}
	\caption{A $256 \times 256$ square defect Gaussian image with/without contamination and after filtering with kernel radius 40. Defected pixels have the distribution $\normal(3,1)$. The square is $30\times 30$ pixels in size. The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$. Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.}
	\label{fig:inference_square2Defect}
\end{figure}

@@

\begin{figure}[htp]
	\centering
		\centerline{
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/Experiment_DefectSimulationDust_roc.eps}
				\caption{ROC area}
			\end{subfigure}
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/Experiment_DefectSimulationDust_type1.eps}
				\caption{Type 1 error}
			\end{subfigure}
		}
		\centerline{
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/Experiment_DefectSimulationDust_type2.eps}
				\caption{Type 2 error}
			\end{subfigure}
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/Experiment_DefectSimulationDust_fdr.eps}
				\caption{FDR}
				\label{fig:inference_DefectSimulationDust_fdr}
			\end{subfigure}
		}
	\caption{ROC area and various errors obtained when conducting hypothesis test on the uncontaminated image, contaminated image and the filtered contaminated image of a $256 \times 256$ salt defect, Gaussian image. The filter used a kernel radius \addNumber{../figures/inference/defectsimulation/Experiment_DefectSimulationDust_radius.txt}. Defected pixels have the distribution $\normal(\mu_1,1)$ where $\mu_1$ was varied in this experiment. The salt defect has density $\pi_1 = 0.1$. The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$. The FDR was controlled at the $2\sigma$ level. The box plot summarise the \addNumber{../figures/inference/defectsimulation/Experiment_DefectSimulationDust_nRepeat.txt} repeats of the experiment. Some contamination plots may have been omitted due to being off the scale.}
	\label{fig:inference_DefectSimulationDust}
\end{figure}

@@

\subsection{Real Data}

>>>>

\section{Literature Review}

@@

@@

@@

@@

\begin{figure}
	\centering
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection_error1.eps}
        \caption{$\mu_0$}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection_error2.eps}
        \caption{$\sigma_0$}
    \end{subfigure}
    \caption{Median squared error of the estimators of the empirical null parameters from 50 repeats of $n$ simulated $\normal(0,1)$ data. Lines represent the rule of thumb for various values of $b$.}
    \label{fig:inference_ZNull1}
\end{figure}

\begin{figure}
	\centering
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection_error3.eps}
        \caption{Heatmap}
    \end{subfigure}
    \caption{Median value of $\widehat{\sigma}_0$ from 50 repeats of $n$ simulated $\normal(0,1)$ data. On the right, lines represent the rule of thumb for various values of $b$. On the left shows the true value of $\sigma_0=1$ as a plane, the empirical truth is where that plan intersects the surface.}
    \label{fig:inference_ZNull2}
\end{figure}

@@

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection2_plot1.eps}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection2_plot51.eps}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection2_plot100.eps}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection2_plot150.eps}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection2_plot199.eps}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/BandwidthSelection2_plot249.eps}
    \end{subfigure}
    }
    \caption{A local quadratic regression was fitted on the log mean squared error for estimating $\sigma_0$ against the bandwidth. The estimator $\widehat{\sigma}_0$ uses the kernel density estimator fitted onto $n$ simulated standard Normal data. Boxplots were used to represent the variation of the error from 50 repeats.}
    \label{fig:inference_ZNull_mse_plot}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.7\textwidth]{../figures/inference/BandwidthSelection2_ruleOfThumb.eps}
	\caption{An identity link Gamma GLM was fitted onto the relationship between the optimal bandwidth and $n^{-1/5}$. The boxplot show the bootstrap error in finding the optimal bandwidth, which is only there for illustration purposes.}
	\label{fig:inference_ZNull_mserule_of_thumb}
\end{figure}

\begin{table}
	\centering
	\input{../figures/inference/BandwidthSelection2_bandwidthEstimate.txt}
	\caption{Estimated and standard error gradient and intercept from the linear relationship in Figure \ref{fig:inference_ZNull_mserule_of_thumb}.}
	\label{table:inference_ZNull_mse_glm_estimate}
\end{table}

@@

@@

@@

In this experiment, a Gaussian image of size $\addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_width.txt} \times \addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_height.txt}$ was simulated. The sample mean and sample variance of the post filtered test statistics were recorded. This was repeated \addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_nrepeat.txt} times by simulating another Gaussian image. Various kernel radiuses from $r = \addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_radius1.txt}$ to $r = \addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_radiusend.txt}$ were investigated.

\begin{figure}[htp]
	\centering
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianEmpirical_mean.eps}
		\caption{Post filter sample mean}
	\end{subfigure}
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussianEmpirical_variance.eps}
		\caption{Post filter sample variance}
	\end{subfigure}
	\caption{The sample mean and sample variance of the test statistics in a filtered Gaussian image of size $\addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_width.txt} \times \addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_height.txt}$. The box plots summarise the \addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_nrepeat.txt} repeats of the experiment. The dotted lines show the critical region at the 2$\sigma$ level using standard tests for the sample mean and sample variance, assuming independence.}
	\label{fig:inference_allnullgaussian}
\end{figure}

@@

An experiment was conducted to investigate the sample mean and sample variance of the filtered contaminated image. Ideally the sample mean and sample variance should be 0 and 1 respectively. Different radiuses were investigated from ??? to ??? and repeated ??? times.

@@

\begin{figure}[htp]
	\centering
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneEmpirical_mean.eps}
		\caption{Post filter sample mean}
	\end{subfigure}
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlaneEmpirical_variance.eps}
		\caption{Post filter sample variance}
	\end{subfigure}
	\caption{The sample mean and sample variance of the test statistics in a filtered contaminated Gaussian image of size $\addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_width.txt} \times \addNumber{../figures/inference/allnull/AllNullGaussianEmpirical_height.txt}$. The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = \addNumber{../figures/inference/contamination/gradx.txt} (x-x_0) + \addNumber{../figures/inference/contamination/grady.txt} (y-y_0)$ and $\sigma_0=\addNumber{../figures/inference/contamination/nullstd.txt}$. The box plots summarise the \addNumber{../figures/inference/allnull/AllNullPlaneEmpirical_nrepeat.txt} repeats of the experiment. The dotted lines show the critical region at the 2$\sigma$ level using standard tests for the sample mean and sample variance, assuming independence.}
	\label{fig:inference_allnullplane}
\end{figure}

@@

\begin{figure}[p]
	\centering
		\centerline{
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare2_imagePreContaminated.eps}
				\caption{Uncontaminated}
			\end{subfigure}
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare2_imageContaminated.eps}
				\caption{Contaminated}
			\end{subfigure}
		}
		\centerline{
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare2_imageFiltered.eps}
				\caption{Filtered}
			\end{subfigure}
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare2_nullStd.eps}
				\caption{Empirical null std}
			\end{subfigure}
		}
	\caption{A $256 \times 256$ square defect Gaussian image with/without contamination and after filtering with kernel radius 40. Defected pixels have the distribution $\normal(3,1)$. The square is $30\times 30$ pixels in size. The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$. Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.}
	\label{fig:inference_square2Defect}
\end{figure}

@@

\begin{figure}[htp]
	\centering
		\centerline{
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDust0Empirical_roc.eps}
				\caption{ROC area}
			\end{subfigure}
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDust0Empirical_type1.eps}
				\caption{Type 1 error}
			\end{subfigure}
		}
		\centerline{
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDust0Empirical_type2.eps}
				\caption{Type 2 error}
			\end{subfigure}
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDust0Empirical_fdr.eps}
				\caption{FDR}
			\end{subfigure}
		}
	\caption{ROC area and various errors obtained when conducting hypothesis test on a \emph{empirical null} filtered image of a $256 \times 256$ salt defected Gaussian image. a) shows the ROC area when testing the image before and after filtering. In b) c) d) the dotted line shows the 95\% empirical confidence interval of the resulting error when testing the image before filtering. The filter used a kernel radius \addNumber{../figures/inference/defectsimulation/DefectAltDustEmpirical_radius.txt}. Defected pixels have the distribution $\normal(\mu_1,1)$ where $\mu_1$ was varied in this experiment. The salt defect has density $\pi_1 = 0.1$. The FDR was controlled at the 5\% level. The box plot summarise the \addNumber{../figures/inference/defectsimulation/DefectAltDustEmpirical_nRepeat.txt} repeats of the experiment.}
\end{figure}

\begin{figure}[htp]
	\centering
		\centerline{
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDust0MadMode_roc.eps}
				\caption{ROC area}
			\end{subfigure}
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDust0MadMode_type1.eps}
				\caption{Type 1 error}
			\end{subfigure}
		}
		\centerline{
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDust0MadMode_type2.eps}
				\caption{Type 2 error}
			\end{subfigure}
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDust0MadMode_fdr.eps}
				\caption{FDR}
			\end{subfigure}
		}
	\caption{ROC area and various errors obtained when conducting hypothesis test on a \emph{MAD mode null} filtered image of a $256 \times 256$ salt defected Gaussian image. a) shows the ROC area when testing the image before and after filtering. In b) c) d) the dotted line shows the 95\% empirical confidence interval of the resulting error when testing the image before filtering. The filter used a kernel radius \addNumber{../figures/inference/defectsimulation/DefectAltDustEmpirical_radius.txt}. Defected pixels have the distribution $\normal(\mu_1,1)$ where $\mu_1$ was varied in this experiment. The salt defect has density $\pi_1 = 0.1$. The FDR was controlled at the 5\% level. The box plot summarise the \addNumber{../figures/inference/defectsimulation/DefectAltDustEmpirical_nRepeat.txt} repeats of the experiment.}
\end{figure}

\begin{figure}[htp]
	\centering
		\centerline{
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDustEmpirical_roc.eps}
				\caption{ROC area}
			\end{subfigure}
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDustEmpirical_type1.eps}
				\caption{Type 1 error}
			\end{subfigure}
		}
		\centerline{
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDustEmpirical_type2.eps}
				\caption{Type 2 error}
			\end{subfigure}
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDustEmpirical_fdr.eps}
				\caption{FDR}
				\label{fig:inference_DefectSimulationDust_fdr}
			\end{subfigure}
		}
	\caption{ROC area and various errors obtained when conducting hypothesis test on a \emph{empirical null} filtered contaminated image of a $256 \times 256$ salt defected Gaussian image. a) shows the ROC area when testing the image before/after contamination and after filtering. In b) c) the dotted line shows the 95\% empirical confidence interval of the resulting error when testing the image before contamination. The filter used a kernel radius \addNumber{../figures/inference/defectsimulation/DefectAltDustEmpirical_radius.txt}. Defected pixels have the distribution $\normal(\mu_1,1)$ where $\mu_1$ was varied in this experiment. The salt defect has density $\pi_1 = 0.1$. The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$. The FDR was controlled at the 5\% level. The box plot summarise the \addNumber{../figures/inference/defectsimulation/DefectAltDustEmpirical_nRepeat.txt} repeats of the experiment.}
	\label{fig:inference_DefectSimulationDust}
\end{figure}

\begin{figure}[htp]
	\centering
		\centerline{
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDustMadMode_roc.eps}
				\caption{ROC area}
			\end{subfigure}
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDustMadMode_type1.eps}
				\caption{Type 1 error}
			\end{subfigure}
		}
		\centerline{
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDustMadMode_type2.eps}
				\caption{Type 2 error}
			\end{subfigure}
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/DefectAltDustMadMode_fdr.eps}
				\caption{FDR}
				\label{fig:inference_DefectSimulationDust_fdr}
			\end{subfigure}
		}
	\caption{ROC area and various errors obtained when conducting hypothesis test on a \emph{MAD mode null} filtered contaminated image of a $256 \times 256$ salt defected Gaussian image. a) shows the ROC area when testing the image before/after contamination and after filtering. In b) c) the dotted line shows the 95\% empirical confidence interval of the resulting error when testing the image before contamination. The filter used a kernel radius \addNumber{../figures/inference/defectsimulation/DefectAltDustEmpirical_radius.txt}. Defected pixels have the distribution $\normal(\mu_1,1)$ where $\mu_1$ was varied in this experiment. The salt defect has density $\pi_1 = 0.1$. The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$. The FDR was controlled at the 5\% level. The box plot summarise the \addNumber{../figures/inference/defectsimulation/DefectAltDustEmpirical_nRepeat.txt} repeats of the experiment.}
\end{figure}

@@

\section{Results}
